---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ECoHeN

<!-- badges: start -->
<!-- badges: end -->

The ECoHeN package is composed many useful functions when working with heterogeneous networks. Functionality includes:

* Extracting communities from a heterogeneous network (ECoHeN) with ECoHeN: `cluster_ECoHeN`,
* Extracting a community from an arbitrary seed set (or list of seed sets): `extract_ECoHeN`
* Extracting statistically significant communities (ESSC) with ESSC: `cluster_ESSC`,
* Refining extracted communities: `refine_ECoHeN`,
* Partitioning a heterogeneous network with ZCMod: `cluster_ZCMod`,
* Evaluating the assortativity of a discovered community: `eval_community`,
* Sampling random heterogeneous networks with the same collection of heterogeneous degree sequences: `sample_heterogeneous_dcm`,
* Sampling random heterogeneous networks with specified block structure: `sample_heterogeneous_sbm`,
* Visualizing the block structure of sampled networks with block structure: `viz_heterogeneous_sbm`,
* Evaluating the overlap between simulated community structure and discovered communities: `eval_jaccard`,
* Converting back and forth between membership vectors (reported by partitioning methods) and a collection of communities (reported by extraction methods).

The extraction procedure of the ECoHeN algorithm in written in C++, and the algorithm can easily be parallelized across initialized seed sets using the `future` package.

## Installation

You can install the development version of ECoHeN from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("ConGibbs10/ECoHeN")
```

## Example Usage

We will recreate the empirical data analysis presented in 



